---
title: "SIA"
output: html_document
date: "2025-11-02"
editor_options: 
  chunk_output_type: console
---
```{r libraries}
library(tidyverse)
library(readxl)
library(car)
library(FSA)
library(writexl)
library(SIBER)
library(ggh4x)
```

# Load SIA Data
```{r sia_df}
sia <- read_xlsx("data/SIA/Stable_Isotope_Data.xlsx") %>%
  dplyr::select(Sample_ID:CN_ratio)

sia$`%N` <- as.numeric(sia$`%N`)

sia_df <- sia %>%
  mutate(
    Depth = case_when(
      str_detect(Sample_ID, "Deep") ~ "Deep",
      str_detect(Sample_ID, "Midd") ~ "Middle",
      str_detect(Sample_ID, "Shall") ~ "Shallow",
      TRUE ~ NA_character_
    ),
    Type = case_when(
      str_detect(Sample_ID, "Host") ~ "Host",
      str_detect(Sample_ID, "Zoox") ~ "Zoox",
      str_detect(Sample_ID, "water") ~ "Water",
      TRUE ~ NA_character_
    ),
    Replicate = if_else(str_detect(Sample_ID, "_r2$|R2$"), "R2", "R1")
  ) 
```

# Compare Replicates
```{r R1 and R2 dfs}
#Separate R1 and R2 to get separate columns and then combine 
R1 <- sia_df %>%
  filter(Replicate == "R1") %>%
  select(Sample_ID, Type, Depth, R1_d15N = d15N, R1_d13C = d13C, R1_CN_ratio = CN_ratio) %>%
  mutate(Sample_ID = str_remove(Sample_ID, "_Host"),
         Sample_ID = str_remove(Sample_ID, "_Zoox"))

R2 <- sia_df %>%
  filter(Replicate == "R2") %>%
  mutate(Sample_ID = str_remove(Sample_ID, "_Host_r2"),
         Sample_ID = str_remove(Sample_ID, "_Zoox_r2")) %>%
  select(Sample_ID, Type, Depth, R2_d15N = d15N, R2_d13C = d13C, R2_CN_ratio = CN_ratio)

rep_comp <- left_join(R1, R2) %>%
  filter(Type != "Water")

```

```{r visualize R1 vs R2 for each sample}
# Check Shallow
ggplot(rep_comp %>% filter(Depth == "Shallow"), aes(x = R1_d13C, y = R2_d13C, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Shallow: Rep Check d13C") +
  theme(legend.position = "bottom")

ggplot(rep_comp %>% filter(Depth == "Shallow"), aes(x = R1_d15N, y = R2_d15N, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Shallow: Rep Check d15N") +
  theme(legend.position = "bottom")

# Check Midd
ggplot(rep_comp %>% filter(Depth == "Middle"), aes(x = R1_d13C, y = R2_d13C, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Middle: Rep Check d13C") +
  theme(legend.position = "bottom")

ggplot(rep_comp %>% filter(Depth == "Middle"), aes(x = R1_d15N, y = R2_d15N, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Middle: Rep Check d15N") +
  theme(legend.position = "bottom")

# Check Deep
ggplot(rep_comp %>% filter(Depth == "Deep"), aes(x = R1_d13C, y = R2_d13C, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Deep: Rep Check d13C") +
  theme(legend.position = "bottom")

ggplot(rep_comp %>% filter(Depth == "Deep"), aes(x = R1_d15N, y = R2_d15N, shape = Type, color = Sample_ID)) +
  geom_point(size = 2) +
  facet_wrap(~Type) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  ggtitle("Deep: Rep Check d15N") +
  theme(legend.position = "bottom")

```

```{r standard deviation between samples}
rep_comp_sd <- rep_comp %>%
  mutate(
    sd_d13C = apply(select(., R1_d13C, R2_d13C), 1, sd, na.rm = TRUE),
    sd_d15N = apply(select(., R1_d15N, R2_d15N), 1, sd, na.rm = TRUE),
    sd_CN_ratio = apply(select(., R1_CN_ratio, R2_CN_ratio), 1, sd, na.rm = TRUE)) 

# Filter sd < 1
rep_comp_sd_filtersd1 <- rep_comp_sd %>%
  filter(sd_d13C < 1,
         sd_CN_ratio < 1)
  
rep_comp_sd_sum_filtersd1 <- rep_comp_sd_filtersd1 %>%
  group_by(Type, Depth) %>%
  summarize(
    mean_sd_d13C = mean(sd_d13C, na.rm = TRUE),
    mean_sd_d15N = mean(sd_d15N, na.rm = TRUE),
    mean_sd_CN_ratio = mean(sd_CN_ratio, na.rm = TRUE)
  )

# Filter sd < 2.5 
rep_comp_sd_filtersd2.5 <- rep_comp_sd %>%
  filter(sd_d13C < 2.5,
         sd_CN_ratio < 2.5)
  
rep_comp_sd_sum_filtersd2.5 <- rep_comp_sd_filtersd2.5 %>%
  group_by(Type, Depth) %>%
  summarize(
    mean_sd_d13C = mean(sd_d13C, na.rm = TRUE),
    mean_sd_d15N = mean(sd_d15N, na.rm = TRUE),
    mean_sd_CN_ratio = mean(sd_CN_ratio, na.rm = TRUE))


# Visualize SD between samples for each group 
# d13C
rep_comp %>%
  mutate(sd_d13C = apply(select(., R1_d13C, R2_d13C), 1, sd, na.rm = TRUE)) %>%
  ggplot(aes(x = Depth, y = sd_d13C, fill = Type)) +
  geom_boxplot(alpha = 0.7) +
  labs(y = "Within-sample SD of δ13C", title = "Analytical precision by Depth and Type") +
  theme_minimal()

# d15N
rep_comp %>%
  mutate(sd_d15N = apply(select(., R1_d15N, R2_d15N), 1, sd, na.rm = TRUE)) %>%
  ggplot(aes(x = Depth, y = sd_d15N, fill = Type)) +
  geom_boxplot(alpha = 0.7) +
  labs(y = "Within-sample SD of δ15N", title = "Analytical precision by Depth and Type") +
  theme_minimal()

# Mean diff R1-R2
rep_comp %>%
  mutate(
    diff_d13C = abs(R1_d13C - R2_d13C),
    diff_d15N = abs(R1_d15N - R2_d15N)
  ) %>%
  group_by(Type, Depth) %>%
  summarize(
    mean_diff_d13C = mean(diff_d13C, na.rm = TRUE),
    mean_diff_d15N = mean(diff_d15N, na.rm = TRUE),
    n = n()
  )
```

# Filter samples with high SD between replicates
```{r sia_df_means_filtersd1 and 2.5}
# SD < 1 means 
sia_df_means_filtersd1 <- rep_comp_sd_filtersd1 %>%
  mutate(mean_d13C = (R1_d13C + R2_d13C)/2) %>%
  mutate(mean_d15N = (R1_d15N + R2_d15N)/2) %>%
  mutate(mean_CN_ratio = (R1_CN_ratio + R2_CN_ratio/2))

# SD < 2.5
sia_df_means_filtersd2.5 <- rep_comp_sd_filtersd2.5 %>%
  mutate(mean_d13C = (R1_d13C + R2_d13C)/2) %>%
  mutate(mean_d15N = (R1_d15N + R2_d15N)/2) %>%
  mutate(mean_CN_ratio = (R1_CN_ratio + R2_CN_ratio/2))
```

# d13C vs d15N
```{r}
# d13C vs d15N
ggplot(sia_df_means_filtersd2.5, 
       aes(x = mean_d13C, y = mean_d15N, color = Depth, shape = Type)) +
  geom_point(aes(shape = Type), size = 3) +
  theme_bw() +
  scale_color_manual(values = c("#00004C", "#11569B", "#56A9DC"))+
  theme(legend.position = "bottom") +
  facet_wrap(~Type, scales = "free") 
```

# Plot C:N Ratio (Figure Plot 1)
```{r CN_ratio}
### Figure Plot 1 ###
Type_labels <- labeller(Type = c("Host" = "Host", "Zoox" = "Symbiont"))

CN_ratio <- ggplot(sia_df_means_filtersd2.5, 
                   aes(x = Depth, y = mean_CN_ratio, fill = Depth)) +
  geom_boxplot(position = position_dodge(1)) +
  scale_fill_manual(values = c("#00004C", "#11569B", "#56A9DC")) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        legend.position = "none",
        axis.text = element_text(size = 9),
        axis.title = element_text(size = 11)) +
  labs(y = "C:N") +
  facet_wrap2(~Type, scales = "free", labeller = Type_labels)

# write_xlsx(sia_df_clean, "data/SIA/sia_means_df_clean.xlsx")

ggsave(
  filename = "Plots/SIA/CN_ratio.pdf",  # Name of the output file
  plot = CN_ratio,                      # Specify the plot to save
  width = 4,                            # Width in inches
  height = 4                            # Height in inches
)

ggsave(
  filename = "Plots/SIA/CN_ratio.png",  # Name of the output file
  plot = CN_ratio,                      # Specify the plot to save
  width = 4,                            # Width in inches
  height = 4                            # Height in inches
)
```

```{r CN ratio stats } 
# Host C:N 
sia_df_host_filtersd1 <- sia_df_means_filtersd1 %>%
  filter(Type == "Host")

sia_df_host_filtersd2.5 <- sia_df_means_filtersd2.5 %>%
  filter(Type == "Host")

# Homogeneity of Variances 
leveneTest(mean_CN_ratio ~ Depth, data = sia_df_host_filtersd1) # no sig diff: p = 0.51
leveneTest(mean_CN_ratio ~ Depth, data = sia_df_host_filtersd2.5) # no sig diff: p = 0.36

aov_host_sd1 <- aov(mean_CN_ratio ~ Depth, data = sia_df_host_filtersd1) # sig diff: p = 0.003
aov_host_sd2.5 <- aov(mean_CN_ratio ~ Depth, data = sia_df_host_filtersd2.5)
summary(aov_host_sd1)
summary(aov_host_sd2.5)

TukeyHSD(aov_host_sd1)
TukeyHSD(aov_host_sd2.5)

#_______________________________________________________________________________#

# Zoox C:N
sia_df_zoox_filtersd1 <- sia_df_means_filtersd1 %>%
  filter(Type == "Zoox")

sia_df_zoox_filtersd2.5 <- sia_df_means_filtersd2.5 %>%
  filter(Type == "Zoox")

# Homogeneity of Variances 
leveneTest(mean_CN_ratio ~ Depth, data = sia_df_zoox_filtersd1) # no sig diff p = 0.77
leveneTest(mean_CN_ratio ~ Depth, data = sia_df_zoox_filtersd2.5) # no sig diff p = 0.72

# Anova 
aov_zoox_sd1 <- aov(mean_CN_ratio ~ Depth, data = sia_df_zoox_filtersd1) # no sig diff: p = 0.68
aov_zoox_sd2.5 <- aov(mean_CN_ratio ~ Depth, data = sia_df_zoox_filtersd2.5) # no sig diff: p 0.65
summary(aov_zoox_sd1)
summary(aov_zoox_sd2.5)
```

# d13C-Host vs d15N-Zoox Carbon (Filtered)
```{r sia_df_combo}
sia_df_combo_filtersd1 <-  sia_df_means_filtersd1 %>% 
  mutate(Depth_Geno = substring(Sample_ID, first = 13)) %>%
  select(Sample_ID, Depth, Depth_Geno, Type, mean_d13C, mean_d15N, mean_CN_ratio) %>%
  pivot_wider(
    id_cols = c(Sample_ID, Depth),
    names_from = Type,
    values_from = starts_with("mean_"),
    names_sep = "_")

sia_df_combo_filtersd2.5 <-  sia_df_means_filtersd2.5 %>% 
  mutate(Depth_Geno = substring(Sample_ID, first = 13)) %>%
  select(Sample_ID, Depth, Depth_Geno, Type, mean_d13C, mean_d15N, mean_CN_ratio) %>%
  pivot_wider(
    id_cols = c(Sample_ID, Depth),
    names_from = Type,
    values_from = starts_with("mean_"),
    names_sep = "_")

ggplot(sia_df_combo_filtersd2.5, aes(x = mean_d13C_Host, y = mean_d13C_Zoox, color = Depth)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("#00004C", "#11569B", "#56A9DC")) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") 

```

# Holobiont means (Filtered)
```{r holo_means}
holo_means_filtersd1 <- rep_comp_sd_filtersd1 %>%
  pivot_wider(
    id_cols = c(Sample_ID, Depth),
    names_from = Type,
    values_from = c(
      R1_d15N, R1_d13C, R1_CN_ratio,
      R2_d15N, R2_d13C, R2_CN_ratio),
    names_glue = "{.value}_{Type}") %>%
  mutate(mean_d13C = (R1_d13C_Host + R2_d13C_Host + R1_d13C_Zoox + R2_d13C_Zoox)/4) %>%
  mutate(mean_d15N = (R1_d15N_Host + R2_d15N_Host + R1_d15N_Zoox + R2_d15N_Zoox)/4) %>%
  mutate(mean_CN = (R1_CN_ratio_Host + R2_CN_ratio_Host + R1_CN_ratio_Zoox + R1_CN_ratio_Zoox)/4) %>%
  select(Sample_ID, Depth, mean_d13C, mean_d15N, mean_CN)

holo_means_filtersd2.5 <- rep_comp_sd_filtersd2.5 %>%
  pivot_wider(
    id_cols = c(Sample_ID, Depth),
    names_from = Type,
    values_from = c(
      R1_d15N, R1_d13C, R1_CN_ratio,
      R2_d15N, R2_d13C, R2_CN_ratio),
    names_glue = "{.value}_{Type}") %>%
  mutate(mean_d13C = (R1_d13C_Host + R2_d13C_Host + R1_d13C_Zoox + R2_d13C_Zoox)/4) %>%
  mutate(mean_d15N = (R1_d15N_Host + R2_d15N_Host + R1_d15N_Zoox + R2_d15N_Zoox)/4) %>%
  mutate(mean_CN = (R1_CN_ratio_Host + R2_CN_ratio_Host + R1_CN_ratio_Zoox + R1_CN_ratio_Zoox)/4) %>%
  select(Sample_ID, Depth, mean_d13C, mean_d15N, mean_CN)

ggplot(holo_means_filtersd2.5, aes(x = mean_d13C, y = mean_d15N, color = Depth, shape = Depth)) +
  geom_point(aes(shape = Depth), size = 3) +
  theme_bw() +
  scale_color_manual(values = c("#00004C", "#11569B", "#56A9DC"))+
  theme(legend.position = "bottom") +
  ggtitle("Holobiont SIA")
```

# Comparing d13C to colony depth (Filtered) (Figure Plot 2)
```{r}
sample_data <- read_xlsx(path = "data/frag_data/2023-AS_NMS_Mgris_collections.xlsx") %>%
  select(Sample_ID = Frag_ID, Depth_Group, Colony_Depth_m) %>%
  filter(!(Sample_ID %in% c("1", "2", "3", "4")))

sia_df_depths_filtersd1 <- left_join(sia_df_means_filtersd1, sample_data, by = "Sample_ID")

sia_df_depths_filtersd2.5 <- left_join(sia_df_means_filtersd2.5, sample_data, by = "Sample_ID")

# Function to calculate standard error
standard_error <- function(x) {
  sd(x) / sqrt(length(x))
}

sia_df_means_sum_filtersd1 <- sia_df_depths_filtersd1 %>%
  group_by(Depth, Type) %>%
  summarize(
    mean_d13C = mean(c(R1_d13C, R2_d13C)),
    se_d13C = standard_error(c(R1_d13C, R2_d13C)),
    mean_d15N = mean(c(R1_d15N, R2_d15N)),
    se_d15N = standard_error(c(R1_d15N, R2_d15N)),
    mean_Colony_Depth = mean(Colony_Depth_m))

sia_df_means_sum_filtersd2.5 <- sia_df_depths_filtersd2.5 %>%
  group_by(Depth, Type) %>%
  summarize(
    mean_d13C = mean(c(R1_d13C, R2_d13C)),
    se_d13C = standard_error(c(R1_d13C, R2_d13C)),
    mean_d15N = mean(c(R1_d15N, R2_d15N)),
    se_d15N = standard_error(c(R1_d15N, R2_d15N)),
    mean_Colony_Depth = mean(Colony_Depth_m))

d13CvDepth <- ggplot(sia_df_depths_filtersd2.5, 
       aes(x = Colony_Depth_m, y = mean_d13C, 
           color = Type, shape = Type)) +
  geom_point(size = 3) +
  geom_smooth(method = lm, se = FALSE) +
  labs(x = "Colony Depth (m)", 
       y = expression(delta^{13}*C)) +
  scale_color_manual(values = c("pink2", "darkgreen"),  
                     labels = c("Host", "Symbiont")) +
  scale_shape_manual(
    values = c("Host" = 16, "Zoox" = 17),  # pick any shapes you like
    labels = c("Host", "Symbiont")) +
  theme_classic() +
  theme(legend.position = c(0.15,0.1),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.box.background = element_blank(),legend.key = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11)) 

ggsave(
  filename = "Plots/SIA/d13CvDepth.pdf",  # Name of the output file
  plot = d13CvDepth,                      # Specify the plot to save
  width = 4,                            # Width in inches
  height = 4                            # Height in inches
)

ggsave(
  filename = "Plots/SIA/d13CvDepth.png",  # Name of the output file
  plot = d13CvDepth,                      # Specify the plot to save
  width = 4,                            # Width in inches
  height = 4                            # Height in inches
)

```

# SIBER Analysis (Filtered < 2.5)
```{r}
# Deep 
siber_df_deep_filtersd2.5 <- sia_df_means_filtersd2.5 %>%
  filter(Depth == "Deep") %>%
  select(iso1 = mean_d13C, iso2= mean_d15N, group = Type,
         community = Depth)

siber_df_deep_filtersd2.5 <- as.data.frame(siber_df_deep_filtersd2.5)

siber_object_deep_filtersd2.5 <- createSiberObject(siber_df_deep_filtersd2.5)

siber_object_deep_plot_filtersd2.5 <- siber_object_deep_filtersd2.5$raw.data$Deep


ggplot(siber_object_deep_plot_filtersd2.5, aes(x = iso1, y = iso2, color = group, fill = group)) +
  
  stat_ellipse(
    geom = "polygon",
    alpha = 0.2,
    level = 0.40) +
  
  geom_point(size = 3) +
  
  scale_color_manual(values = c("Host" = "pink2",
                                "Zoox" = "darkgreen")) +
  scale_fill_manual(values = c("Host" = "pink2",
                               "Zoox" = "darkgreen")) +
  
  labs(
    x = expression(delta^13*C~"\u2030"),
    y = expression(delta^15*N~"\u2030")
  ) +
  
  theme_classic()
```

```{r}
# Middle 
siber_df_midd_filtersd2.5 <- sia_df_means_filtersd2.5 %>%
  filter(Depth == "Middle") %>%
  select(iso1 = mean_d13C, iso2= mean_d15N, group = Type,
         community = Depth)

siber_df_midd_filtersd2.5 <- as.data.frame(siber_df_midd_filtersd2.5)

siber_object_midd_filtersd2.5 <- createSiberObject(siber_df_midd_filtersd2.5)

siber_object_midd_plot_filtersd2.5 <- siber_object_midd_filtersd2.5$raw.data$Middle

ggplot(siber_object_midd_plot_filtersd2.5, aes(x = iso1, y = iso2, color = group, fill = group)) +
  
  stat_ellipse(
    geom = "polygon",
    alpha = 0.2,
    level = 0.40) +
  
  geom_point(size = 3) +
  
  scale_color_manual(values = c("Host" = "pink2",
                                "Zoox" = "darkgreen")) +
  scale_fill_manual(values = c("Host" = "pink2",
                               "Zoox" = "darkgreen")) +
  
  labs(
    x = expression(delta^13*C~"\u2030"),
    y = expression(delta^15*N~"\u2030")
  ) +
  
  theme_classic()
```

```{r}
# Shallow 
siber_df_shal_filtersd2.5 <- sia_df_means_filtersd2.5 %>%
  filter(Depth == "Shallow") %>%
  select(iso1 = mean_d13C, iso2= mean_d15N, group = Type,
         community = Depth)

siber_df_shal_filtersd2.5 <- as.data.frame(siber_df_shal_filtersd2.5)

siber_object_shal_filtersd2.5 <- createSiberObject(siber_df_shal_filtersd2.5)

siber_object_shal_plot_filtersd2.5 <- siber_object_shal_filtersd2.5$raw.data$Shallow

ggplot(siber_object_shal_plot_filtersd2.5, aes(x = iso1, y = iso2, color = group, fill = group)) +
  
  stat_ellipse(
    geom = "polygon",
    alpha = 0.2,
    level = 0.40) +
  
  geom_point(size = 3) +
  
  scale_color_manual(values = c("Host" = "pink2",
                                "Zoox" = "darkgreen")) +
  scale_fill_manual(values = c("Host" = "pink2",
                               "Zoox" = "darkgreen")) +
  
  labs(
    x = expression(delta^13*C~"\u2030"),
    y = expression(delta^15*N~"\u2030")
  ) +
  
  theme_classic()
```

```{r}
siber_df_all <- sia_df_means_filtersd2.5 %>%
  select(iso1 = mean_d13C, iso2= mean_d15N, group = Type,
         community = Depth)

siber_df_all <- as.data.frame(siber_df_all)

siber_object_all <- createSiberObject(siber_df_all)

siber_object_all_plot <- siber_object_all$original.data

siber_plot <- ggplot(siber_object_all_plot, aes(x = iso1, y = iso2, color = group, fill = group)) + 
  geom_point(size = 3) + 
  stat_ellipse(geom = "polygon",
    alpha = 0.2,
    level = 0.40) + 
  scale_color_manual(values = c("Host" = "pink2",
                                "Zoox" = "darkgreen"),
                     labels = c("Host", "Symbiont")) +
  scale_fill_manual(values = c("Host" = "pink2",
                               "Zoox" = "darkgreen"),
                               labels = c("Host", "Symbiont")) + 
  labs(
    x = expression(delta^13*C~"\u2030"),
    y = expression(delta^15*N~"\u2030")) + 
  theme_bw() +
  facet_wrap(~community) +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11),
        strip.text = element_text(size = 12)) 

ggsave(
  filename = "Plots/SIA/siber_plot.pdf",  # Name of the output file
  plot = siber_plot,                      # Specify the plot to save
  width = 8,                            # Width in inches
  height = 3.5                            # Height in inches
)

ggsave(
  filename = "Plots/SIA/siber_plot.png",  # Name of the output file
  plot = siber_plot,                      # Specify the plot to save
  width = 8,                            # Width in inches
  height = 3.5                            # Height in inches
)

```

```{r}
library(ggpubr)

top <- ggarrange(CN_ratio,d13CvDepth,
          ncol = 2,
          align = "hv",
          labels = c("A", "B"))

bottom <- ggarrange(siber_plot,
          labels = c("C"))

Fig_3 <- ggarrange(top, bottom, ncol = 1,
          align = "hv")
ggsave(
  filename = "Plots/SIA/Fig_3.pdf",  # Name of the output file
  plot = Fig_3,                      # Specify the plot to save
  width = 8,                            # Width in inches
  height = 6.5                            # Height in inches
  )
  
  
ggsave(
  filename = "Plots/SIA/Fig_3.png",  # Name of the output file
  plot = Fig_3,                      # Specify the plot to save
  width = 8,                            # Width in inches
  height = 6.5                            # Height in inches
)
```

